---
title: "Cleaning Data"
format: html
editor: visual
---

## Prepping

Clearing the environment, loading the libraries and saving the path to the data folder.

```{r}
#| message: false
rm(list = ls())

library(tidyverse)
library(stringr)
library(dplyr)
#library(ggbeeswarm)

data_path <- "~/projects/Group25_Project/data"
```

### Loading the data

```{r}
#| message: false

data_aug_path <- file.path(data_path, "03_dat_aug.RDS")
data_aug <- read_rds(file = data_aug_path)

```

### Reducing to only paired data

```{r}
paired_data <- data_aug |> 
  filter(p < 0.001 & log_fold_change > 2) |>
  group_by(sample_ID, cohort, HLA, peptide) |>
  filter(any(KIR_blocking == 0) & any(KIR_blocking == 1))

```

### **Plotting count for each paired, significant peptide**

```{r}

paired_data |> 
  ggplot(aes(x = peptide,
             y = count,
             color = KIR_blocking,
             shape = cohort)) +
  geom_point() +
  facet_grid(. ~ HLA,
             scales = "free_x",
             space = "free_x") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
  

```

### **Plotting count fraction for each paired, significant peptide**

```{r}

paired_data |> 
  ggplot(aes(x = peptide,
             y = count_fraction,
             color = KIR_blocking,
             shape = cohort)) +
  geom_point() +
  facet_grid(. ~ HLA,
             scales = "free_x",
             space = "free_x") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
  

```

### Plotting count fraction for each cohort, in the paired dataset

```{r}

paired_data |> 
  ungroup() |>
  ggplot(aes(x = KIR_blocking,
             y = count_fraction,
             color = sample_ID,
             shape = HLA)) +
  geom_point(size = 2.5) +
  facet_grid(. ~ cohort,
             scales = "free_x",
             space = "free_x")

```

### 
Plotting count fraction for each cohort, all data

```{r}

data_aug |> 
  ungroup() |>
  ggplot(aes(x = KIR_blocking,
             y = count_fraction)) +
  geom_point(size = 2.5,
             position = position_dodge2(w = 0.5)) +
  facet_grid( HLA ~ cohort,
             scales = "free_x",
             space = "free_x")

```
